Unshuffling Permutations

### 2016-02-03 new-article.tex
LATIN 2016

\newcommand{\CrossingLL}{%
\begin{tikzpicture}[scale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,4) $) and ($ (U3.north) + (0,4) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,4) $) and ($ (U4.north) + (0,4) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingLL

@@

@@

@@

\newcommand{\LabeledInclusionLL}[4]{%
\begin{tikzpicture}[scale=0.25,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#1};
\draw node [] [right of=U1] (U2) {#2};
\draw node [] [right of=U2] (U3) {#3};
\draw node [] [right of=U3] (U4) {#4};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLL

@@

\newcommand{\LabeledInclusionLR}[4]{%
\begin{tikzpicture}[scale=0.25,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#1};
\draw node [] [right of=U1] (U2) {#2};
\draw node [] [right of=U2] (U3) {#3};
\draw node [] [right of=U3] (U4) {#4};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLR

@@

\newcommand{\LabeledInclusionRL}[4]{%
\begin{tikzpicture}[scale=0.25,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#1};
\draw node [] [right of=U1] (U2) {#2};
\draw node [] [right of=U2] (U3) {#3};
\draw node [] [right of=U3] (U4) {#4};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRL

@@

\newcommand{\LabeledInclusionRR}[4]{%
\begin{tikzpicture}[scale=0.25,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#1};
\draw node [] [right of=U1] (U2) {#2};
\draw node [] [right of=U2] (U3) {#3};
\draw node [] [right of=U3] (U4) {#4};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRR

@@

@@

@@

@@

@@

\begin{proof}[of Lemma~\ref{lemma:matching}]
    (\emph{1} $\Rightarrow$ \emph{2}).
    Since $\pi$ is a square, it admits a square root, say $\sigma$.
    Let $2n = |\pi|$ (and hence $|\sigma| = n$).
    Then, by definition, there exist two sets
    $I^1 = \{i^1_1 < i^1_2 < \dots < i^1_n\}$
    and $I^2 = \{i^2_1 < i^2_2 < \dots < i^2_n\}$ of disjoint indexes of
    letters of $\pi$ such that $\pi_{|I^1}$ and $\pi_{|I^2}$ are both
    order-isomorphic to $\sigma$.
    Let $G_\pi$ be the linear clique associated to $\pi$ with vertices
    $\VS{G_\pi} = \{i^1_j : j \in [n]\} \cup \{i^2_j : j \in [n]\}$.
    Define $\vv{\mathcal{M}} = \{(i^1_j, i^2_j) : j \in [n]\}$.
    It is easily seen that $\vv{\mathcal{M}}$ is an oriented perfect
    matching since $I^1 \cap I^2 = \emptyset$, and
    $I^1 \cup I^2 = \{1, 2,  \dots 2n\}$.
    It also avoids \InclusionLL,~\InclusionLR,~\InclusionRL and \InclusionRR.
    Indeed, suppose, aiming at a contradiction, that such a bad configuration exists
    for arcs $(i^1_j, i^2_j)$ and $(i^1_k, i^2_k)$ of $\vv{\mathcal{M}}$
    with $j < k$.
    \begin{itemize}
      \item
      \LabeledInclusionLL{$i^1_j$}{$i^1_k$}{$i^2_k$}{$i^2_j$}
      \item
      \LabeledInclusionLL{$i^1_j$}{$i^1_k$}{$i^2_k$}{$i^2_j$}
      \item
      \LabeledInclusionLL{$i^1_j$}{$i^1_k$}{$i^2_k$}{$i^2_j$}
      \item
      \LabeledInclusionLL{$i^1_j$}{$i^1_k$}{$i^2_k$}{$i^2_j$}
    \end{itemize}

    Indeed, if it is not the case then there would exist two edges
    $e = \{i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$, $j < k$, in
    $\mathcal{M}$ such that $i^1_j < i^1_k < i^2_k < i^2_j$ or
    $i^1_j < i^2_k < i^1_k < i^2_j$. This is a contradiction since
    $i^2_k > i^2_j$ if $k > j$. Finally, for any two distinct edges
    $e = \{\i^1_j, i^2_j\}$ and $e' = \{i^1_k, i^2_k\}$ of $\mathcal{M}$,
    we have $\pi(i^1_j) < \pi(i^2_j)$ if and only if
    $\pi(i^1_k) < \pi(i^2_k)$ since we are comparing in both cases two
    elements (at position $j$ and $k$) in two patterns that are
    order-isomorphic to $\sigma$.

    (\emph{2} $\Rightarrow$ \emph{1}).
    Let $I^1 = \{i^1_j : \exists \{i_j, i_k\} \in \mathcal{M}
    \;\text{with}\; j < k\}$, and
    $I^2 = \{i^2_k : \exists \{i_j, i_k\} \in \mathcal{M}
    \;\text{with}\; j < k\}$.
    Informally, $I^1$ (resp. $I^2$) is the set of the left (resp. right)
    endpoints of the edges in $\mathcal{M}$ assuming the positions
    $1, 2, \dots, 2$ are drawn along an horizontal line.
    Without loss of generality, assume $i^1_1 < i^1_2 < \dots < i^1_n$.
    % and $I^2 = \{i^2_1, i^2_2, \dots, i^2_n\}$.
    Let $p^1 = \pi(i^1_1) \pi(i^1_2) \dots \pi(i^1_n)$ and
    $p^2 = \pi(i^2_1) \pi(i^2_2) \dots \pi(i^2_n)$ be the two patterns
    from $\pi$ induced by $I^1$ and $I^2$, respectively. Clearly $p^1$
    and $p^2$ are disjoint in $\pi$ (since $\mathcal{M}$ is a matching)
    and cover $\pi$ (since $\mathcal{M}$ is perfect). We also claim that
    $p^1$ and $p^2$ are order-isomorphic. Suppose, aiming at a
    contradiction, that this is not the case. Therefore, there exist two
    positions $j$ and $k$, say $j < k$, such that
    $\pi(i^1_j) < \pi(i^2_j)$ and $\pi(i^1_k) > \pi(i^2_k)$, or
    $\pi(i^1_j) < \pi(i^2_j)$ and $\pi(i^1_k) > \pi(i^2_k)$.
    But since $\mathcal{M}$ is containment-free, it follows that both
    $\{i^1_j, i^2_j\}$, $i^1_j < i^2_j$, and $\{i^1_k, i^2_k\}$,
    $i^1_k, i^2_k$, belong to $\mathcal{M}$. This is a contradiction
    since for any two distinct edges $(a, b)$ and $(a', b')$ in
    $\mathcal{M}$ we have $\pi(a) < \pi(a')$ if and only if
    $\pi(b) < \pi(b')$.
    \qed
\end{proof}

>>>>

\newcommand{\LabeledCrossingLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']%,>=stealth',->]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingLL

\newcommand{\CrossingLL}{%
\begin{tikzpicture}[scale=0.09,inner sep=.8pt,node distance=.25cm,>=latex']%,>=stealth',->]
\draw node [draw,circle,fill=black] (U1)               {};
\draw node [draw,circle,fill=black] [right of=U1] (U2) {};
\draw node [draw,circle,fill=black] [right of=U2] (U3) {};
\draw node [draw,circle,fill=black] [right of=U3] (U4) {};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U3.north) + (0,2) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\end{tikzpicture}
}% end \CrossingLL

\newcommand{\LabeledCrossingLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']%,>=stealth',->]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingLR

@@

\newcommand{\LabeledCrossingRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']%,>=stealth',->]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingRL

@@

\newcommand{\LabeledCrossingRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']%,>=stealth',->]
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U3.north) + (0,1.5) $) .. (U3.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \LabeledCrossingRR

@@

\newcommand{\LabeledInclusionLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLL

@@

\newcommand{\LabeledInclusionLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionLR

@@

\newcommand{\LabeledInclusionRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [->] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRL

@@

\newcommand{\LabeledInclusionRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,2) $) and ($ (U4.north) + (0,2) $) .. (U4.north);
\draw [<-] (U2.north) .. controls ($ (U2.north) + (0,1) $) and ($ (U3.north) + (0,1) $) .. (U3.north);
\end{tikzpicture}
}% end \LabeledInclusionRR

@@

\newcommand{\LabeledPrecedenceLL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLL

@@

\newcommand{\LabeledPrecedenceLR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [->] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceLR

@@

\newcommand{\LabeledPrecedenceRL}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [->] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRL

@@

\newcommand{\LabeledPrecedenceRR}[5]{%
\begin{tikzpicture}[scale=#1,inner sep=.8pt,node distance=.45cm,>=latex']
\draw node [] (U1)               {#2};
\draw node [] [right of=U1] (U2) {#3};
\draw node [] [right of=U2] (U3) {#4};
\draw node [] [right of=U3] (U4) {#5};
\draw [<-] (U1.north) .. controls ($ (U1.north) + (0,1.5) $) and ($ (U2.north) + (0,1.5) $) .. (U2.north);
\draw [<-] (U3.north) .. controls ($ (U3.north) + (0,1.5) $) and ($ (U4.north) + (0,1.5) $) .. (U4.north);
\end{tikzpicture}
}% end \PrecedenceRR

@@

\begin{proof}[of Lemma~\ref{lemma:matching}]
    (\emph{1} $\Rightarrow$ \emph{2}).
    Since $\pi$ is a square, it admits a square root, say $\sigma$.
    Let $2n = |\pi|$ (and hence $|\sigma| = n$).
    Then, by definition, there exist two sets
    $I^1 = (i^1_1 < i^1_2 < \dots < i^1_n)$
    and $I^2 = (i^2_1 < i^2_2 < \dots < i^2_n)$ of disjoint indexes of
    letters of $\pi$ such that $\pi_{|I^1}$ and $\pi_{|I^2}$ are both
    order-isomorphic to $\sigma$.
    Let $G_\pi$ be the linear clique associated to $\pi$ with vertices
    $\VS{G_\pi} = \{i^1_j : j \in [n]\} \cup \{i^2_j : j \in [n]\}$.
    Define $\vv{\mathcal{M}} = \{(i^1_j, i^2_j) : j \in [n]\}$.
    It is easily seen that $\vv{\mathcal{M}}$ is an oriented perfect
    matching since $I^1 \cap I^2 = \emptyset$, and
    $I^1 \cup I^2 = \{1, 2,  \dots 2n\}$.
    We first show that it avoids
    \InclusionLL,~\InclusionLR,~\InclusionRL and \InclusionRR.
    Indeed, suppose, aiming at a contradiction, that such a bad configuration exists
    for, say,  arcs $(i^1_j, i^2_j)$ and $(i^1_k, i^2_k)$ of $\vv{\mathcal{M}}$.
    Assuming $i^1_j < i^1_k$ we are left with the following $4$ configurations:
    \begin{center}
      \begin{tabular}{cccc}
        \LabeledInclusionLL{.3}{$i^1_j$}{$i^1_k$}{$i^2_k$}{$i^2_j$}
        &\qquad
        \LabeledInclusionLR{.3}{$i^1_j$}{$i^2_k$}{$i^1_k$}{$i^2_j$}
        &\qquad
        \LabeledInclusionRL{.3}{$i^2_k$}{$i^1_j$}{$i^2_j$}{$i^1_k$}
        &\qquad
        \LabeledInclusionRR{.3}{$i^2_k$}{$i^2_j$}{$i^1_j$}{$i^1_k$}
      \end{tabular}
    \end{center}
    Then it follows that $i^2_j > i^2_k$.
    This is a contradiction since
    $i^1_j < i^1_k \Rightarrow j < k \Rightarrow i^2_j < i^2_k$.
    We now turn to proving that $\vv{\mathcal{M}}$ also avoids
    \CrossingLR and \CrossingRL.
    Indeed, suppose, aiming at a contradiction, that such a bad configuration exists
    for, say,  arcs $(i^1_j, i^2_j)$ and $(i^1_k, i^2_k)$ of $\vv{\mathcal{M}}$.
    Assuming $i^1_j < i^1_k$ we are left with the following $2$ configurations:
    \begin{center}
      \begin{tabular}{cccc}
        \LabeledCrossingLR{.3}{$i^1_j$}{$i^2_k$}{$i^2_j$}{$i^1_k$}
        &\qquad
        \LabeledCrossingRL{.3}{$i^2_k$}{$i^1_j$}{$i^1_k$}{$i^2_j$}
      \end{tabular}
    \end{center}
    Then it follows that $i^2_j > i^2_k$.
    Again, this is a contradiction since
    $i^1_j < i^1_k \Rightarrow j < k \Rightarrow i^2_j < i^2_k$.
    Finally, for any two distinct arcs
    $(i^1_j, i^2_j)$ and $(i^1_k, i^2_k)$ of $\vv{\mathcal{M}}$,
    we have $\pi(i^1_j) < \pi(i^2_j)$ if and only if
    $\pi(i^1_k) < \pi(i^2_k)$ since we are comparing in both cases two
    elements (at position $j$ and $k$) in two patterns that are
    order-isomorphic to $\sigma$.

    (\emph{2} $\Rightarrow$ \emph{1}).
    Let $I^1 = (i^1_1 < i^1_2 < \dots < i^1_n)$
    (resp. $I^2 = (i^2_1 < i^2_2 < \dots < i^2_n)$)
    be the ordered sequence of the origins (resp. sinks) of the arcs of
    the oriented perfect matching $\vv{\mathcal{M}}$.
    We first show that, for every $1 \leq j \leq n$,
    $(i^1_j, i^2_j)$ is an arc of $\vv{\mathcal{M}}$.
    The proof is by induction on $n$.
    Since the assertion is certainly valid for $n = 1$,
    it is enough to show that $(i^1_n, i^2_n)$ is an arc of $\vv{\mathcal{M}}$.
    Suppose, aiming at a contradiction that $(i^1_n, i^2_n)$
    is not an arc of $\vv{\mathcal{M}}$.
    Let $i^2_p$ be the sink of the arc with origin $i^1_n$ in
    $\vv{\mathcal{M}}$ (\emph{i.e.}, $(i^1_n, i^2_p)$ is an abstractof
    $\vv{\mathcal{M}}$).
    We need to consider two cases.
    \begin{itemize}
      \item If $i^1_n > i^2_p$ then there exist $i^1_q$ and $i^2_r$ such
      that
      \begin{center}
        \begin{tabular}{ccc}
          \LabeledInclusionRL{.3}{$i^2_p$}{$i^1_q$}{$i^2_r$}{$i^1_n$}
          &\qquad
          \LabeledInclusionRR{.3}{$i^1_p$}{$i^2_r$}{$i^1_q$}{$i^1_n$}
          &\qquad
          \LabeledCrossingLR{.3}{$i^1_p$}{$i^2_p$}{$i^2_r$}{$i^1_n$}
        \end{tabular}
      \end{center}
      This is a contradiction since
      $\vv{\mathcal{M}}$ avoids
      \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR and
      \CrossingRL.
      \item
      If $i^1_n < i^2_p$ then there exist $i^1_q$ and $i^2_r$ such
      that
      \begin{center}
        \begin{tabular}{ccc}
          \LabeledInclusionLL{.3}{$i^1_q$}{$i^1_n$}{$i^2_p$}{$i^2_r$}
          &\qquad
          \LabeledInclusionRL{.3}{$i^2_r$}{$i^1_n$}{$i^2_p$}{$i^1_q$}
          &\qquad
          \LabeledCrossingRL{.3}{$i^2_p$}{$i^1_q$}{$i^1_n$}{$i^2_r$}
        \end{tabular}
      \end{center}
      This is a contradiction since
      $\vv{\mathcal{M}}$ avoids
      \InclusionLL,~\InclusionLR,~\InclusionRL,~\InclusionRR,~\CrossingLR and
      \CrossingRL.
    \end{itemize}
    Then it follows that $(i^1_n, i^2_n)$ is an arc
    of $\vv{\mathcal{M}}$.
    Now, let $p^1 = \pi(i^1_1) \pi(i^1_2) \dots \pi(i^1_n)$ and
    $p^2 = \pi(j^2_1) \pi(^2_2) \dots \pi(i^2_n)$ be the two patterns
    from $\pi$ induced by $I^1$ and $I^2$, respectively.
    Clearly $p^1$ and $p^2$ are disjoint in $\pi$
    (since $\vv{\mathcal{M}}$ is a matching)
    and cover $\pi$ (since $\vv{\mathcal{M}}$ is perfect).
    We claim that $p^1$ and $p^2$ are order-isomorphic.
    Indeed, this is a direct consequence of th fact that,
    for any two distinct edges $(a, b)$ and $(a', b')$ in
    $\vv{\mathcal{M}}$ we have $\pi(a) < \pi(a')$ if and only if
    $\pi(b) < \pi(b')$.
    \qed
\end{proof}
